The \emph{FrobeniusThresholds} package for \emph{Macaulay2}

### 2019-12-06 Fsing/FrobeniusThresholdsPaper/FrobeniusThresholds.tex
Updated paper as per referee's comments

@@

At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.  It is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.  Thus, the package could be improved by finalizing and implementing such an algorithm.

>>>>

\noindent \textcolor{red}{Alternative to the next two paragraphs:}

\textcolor{blue}{Within the \emph{TestIdeals} package, the functions \texttt{testIdeal} and \texttt{FPureModule} are used to compute the test ideals of $f$ at different parameters.
By comparing test ideals of $f$ at different parameters, we can decide  whether $t$ is the $F$-pure threshold of $f$. 
Since not only the $F$-pure thresholds, but also the higher $F$-jumping numbers, are determined by containment conditions on test ideals, the functionality is extended to determine whether a given number is an $F$-jumping number.}

@@

At the moment, the specialized algorithm called by the \texttt{fpt} function for computing the $F$-pure threshold of a homogeneous polynomial in two variables limits us to working with the standard grading on the ambient polynomial ring.  It is desirable to be able to work with nonstandard gradings as well, and results of \cite{HernandezTeixeiraFThresholdFunctions} suggest an algorithm for doing so.  For instance, the polynomial $f = x^6+x^2 y^2 + y^3$ is homogeneous under the grading $\deg x = 1, \deg y = 2$, and it is shown that the $F$-threshold of $f$ with respect to the ideal $\langle x, y^2 \rangle$ can be computed as the $F$-pure threshold of $x^3 + x^2 y + y^2$, which is homogeneous under the standard grading.
The package could be improved by finalizing and implementing such an algorithm in greater generality.
